---
title: "Group Differences"
date: "Last updated on `r Sys.Date()`"
author: "Irene"
output:
  html_document: 
    # code_folding: show
    df_print: kable
    highlight: tango
    number_sections: yes
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: yes
---
```{r setup, include=FALSE}
library(tidyverse)
library(DescTools)
library(stats)
library(car)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

data <- read.csv(file = "./Data/SecondStep_Nov_30.csv") %>%
  mutate(MullingStarts_Seconds = ifelse(MullingStarts_Seconds == 0, 0.01, MullingStarts_Seconds))

# For sp st fall 2020
  
d_abint <- data %>%
  filter(group == "ab/int")      #%>%  mutate(at_lethality = mean(X12.18_Injuries_LethalityScale, na.rm = TRUE)) Not included for now

d_at <- data %>%
  filter(group == "at")          #%>%  mutate(at_lethality = mean(X12.18_Injuries_LethalityScale, na.rm = TRUE))
```

 #1:5x,1.5,2:5x,2.5, = 12    3:7x, 4:7x, 4.5:2x = 16

d_at_l <- d_at %>%
  filter(X12.18_Injuries_LethalityScale >= 3) %>%
  mutate(at_lethality = mean(X12.18_Injuries_LethalityScale, na.rm = TRUE))

d_at_nl <- d_at %>%
  filter(X12.18_Injuries_LethalityScale < 3) %>%
  mutate(at_lethality = mean(X12.18_Injuries_LethalityScale, na.rm = TRUE))

d_at_groups <- rbind(d_at_l, d_at_nl) 
d_at_groups <- d_at_groups %>%
  mutate(at_groups = ifelse(at_lethality == 3.625, "at_l", "at-nl"))


```{r}
descriptives <- function(col){
  print(mean(col, na.rm = TRUE))
  print(sd(col, na.rm = TRUE))
}

# use of SD assumes distribution is normal, so let's test if they're normal
qplot(d_abint$Age)
describe(d_abint$Age)
descriptives(d_abint$Age)
shapiro.test(d_abint$Age) # <.001 the distribution is not normal

qplot(d_at$Age)
sd(d_abint$Age)
descriptives(d_at$Age)
shapiro.test(d_at$Age) # <.001 the distribution is not normal

# use of classical t-test assumes equal variance, so let's test if they have equal variance using levene's test
# Levene's test with one independent variable
leveneTest(Age ~ group, data = data) 
# F > .05, no evidence the variabilities are different for two groups

# they are not normal, so we will use classical t-test with pooled variance
t.test(Age~group,data = data, var.equal = TRUE)


# Same for percentage of female sex
data_sex_numeric <- data %>%
  mutate(sex_num = ifelse(sex == "F", 1, 0))
leveneTest(sex_num ~ group, data = data_sex_numeric) # F> .05
t.test(sex_num~group,data = data_sex_numeric, var.equal = TRUE)
d_abint %>%
  filter(race == "African American") #23
```


```{r Usebin}
leveneTest(ThoughtsStart_bin ~ group, data = data) # F > .05
leveneTest(Mull_bin ~ group, data = data)          # F > 
leveneTest(Decision_bin ~ group, data = data)      #   >
leveneTest(FirstMethod_bin ~ group, data = data)   #   >
leveneTest(SureMethod_bin ~ group, data = data)    #   >
leveneTest(FirstPlace_bin ~ group, data = data)    #   >
leveneTest(SurePlace_bin ~ group, data = data)     #   >

t.test(ThoughtsStart_bin ~ group,data = data, var.equal = TRUE)
sd(d_at$ThoughtsStart_bin, na.rm = TRUE)
sd(d_abint$ThoughtsStart_bin, na.rm = TRUE)

t.test(Mull_bin ~ group,data = data, var.equal = TRUE)  #***
sd(d_at$Mull_bin, na.rm = TRUE)
sd(d_abint$Mull_bin, na.rm = TRUE)

t.test(Decision_bin ~ group,data = data, var.equal = TRUE)
sd(d_at$Decision_bin, na.rm = TRUE)
sd(d_abint$Decision_bin, na.rm = TRUE)

t.test(FirstMethod_bin ~ group, data = data, var.equal = TRUE) # p<.07
sd(d_at$FirstMethod_bin, na.rm = TRUE)
sd(d_abint$FirstMethod_bin, na.rm = TRUE)

t.test(SureMethod_bin ~ group, data = data, var.equal = TRUE) # p< .09
sd(d_at$SureMethod_bin, na.rm = TRUE)
sd(d_abint$ThoughtsStart_bin, na.rm = TRUE)

t.test(FirstPlace_bin ~ group, data = data, var.equal = TRUE)
sd(d_at$FirstPlace_bin, na.rm = TRUE)
sd(d_abint$FirstPlace_bin, na.rm = TRUE)

t.test(SurePlace_bin ~ group, data = data, var.equal = TRUE) # *
sd(d_at$SurePlace_bin, na.rm = TRUE)
sd(d_abint$SurePlace_bin, na.rm = TRUE)
```

```{r Useoriginal}
leveneTest(ThoughtsStart_Seconds ~ group, data = data) # F > .05
leveneTest(MullingStarts_Seconds ~ group, data = data) # F > 
leveneTest(Decision_Seconds ~ group, data = data)      #   >
leveneTest(FirstMethod_Seconds ~ group, data = data)   #   >
leveneTest(SureMethod_Seconds ~ group, data = data)    #   >
leveneTest(FirstPlace_Seconds ~ group, data = data)    #   >
leveneTest(SurePlace_Seconds ~ group, data = data)     #   >

t.test(ThoughtsStart_Seconds ~ group, data = data, var.equal = TRUE)
sd(d_at$ThoughtsStart_Seconds, na.rm = TRUE)
sd(d_abint$ThoughtsStart_Seconds, na.rm = TRUE)

t.test(MullingStarts_Seconds ~ group,data = data, var.equal = TRUE) # p< .08
sd(d_at$MullingStarts_Seconds, na.rm = TRUE)
sd(d_abint$MullingStarts_Seconds, na.rm = TRUE)

t.test(Decision_Seconds ~ group, data = data, var.equal = TRUE)   # p<.07
sd(d_at$Decision_Seconds, na.rm = TRUE)
sd(d_abint$Decision_Seconds, na.rm = TRUE)

t.test(FirstMethod_Seconds ~ group, data = data, var.equal = TRUE)
sd(d_at$FirstMethod_Seconds, na.rm = TRUE)
sd(d_abint$FirstMethod_Seconds, na.rm = TRUE)

t.test(SureMethod_Seconds ~ group, data = data, var.equal = TRUE)
sd(d_at$SureMethod_Seconds, na.rm = TRUE)
sd(d_abint$SureMethod_Seconds, na.rm = TRUE)

t.test(FirstPlace_Seconds ~ group, data = data, var.equal = TRUE)
sd(d_at$FirstPlace_Seconds, na.rm = TRUE)
sd(d_abint$FirstPlace_Seconds, na.rm = TRUE)

t.test(SurePlace_Seconds ~ group, data = data, var.equal = TRUE)
sd(d_at$SurePlace_Seconds, na.rm = TRUE)
sd(d_abint$SurePlace_Seconds, na.rm = TRUE)
```

```{r Uselog}
leveneTest(log(ThoughtsStart_Seconds) ~ group, data = data) # F > .05
leveneTest(log(MullingStarts_Seconds) ~ group, data = data) #   ***
leveneTest(log(Decision_Seconds) ~ group, data = data)      #   >
leveneTest(log(FirstMethod_Seconds) ~ group, data = data)   #   >
leveneTest(log(SureMethod_Seconds) ~ group, data = data)    #   >
leveneTest(log(FirstPlace_Seconds) ~ group, data = data)    #   >
leveneTest(log(SurePlace_Seconds) ~ group, data = data)     #   >

t.test(log(ThoughtsStart_Seconds) ~ group, data = data, var.equal = TRUE)
sd(log(d_at$ThoughtsStart_Seconds), na.rm = TRUE)
sd(log(d_abint$ThoughtsStart_Seconds), na.rm = TRUE)

t.test(log(MullingStarts_Seconds) ~ group, data = data, var.equal = FALSE) # ***
sd(log(d_at$MullingStarts_Seconds), na.rm = TRUE)
sd(log(d_abint$MullingStarts_Seconds), na.rm = TRUE)
   
t.test(log(Decision_Seconds) ~ group, data = data, var.equal = TRUE)
sd(log(d_at$Decision_Seconds), na.rm = TRUE)
sd(log(d_abint$Decision_Seconds), na.rm = TRUE)

t.test(log(FirstMethod_Seconds) ~ group, data = data, var.equal = TRUE)  # p< .07
sd(log(d_at$FirstMethod_Seconds), na.rm = TRUE)
sd(log(d_abint$FirstMethod_Seconds), na.rm = TRUE)

t.test(log(SureMethod_Seconds) ~ group, data = data, var.equal = TRUE)
sd(log(d_at$SureMethod_Seconds), na.rm = TRUE)
sd(log(d_abint$SureMethod_Seconds), na.rm = TRUE)

t.test(log(FirstPlace_Seconds) ~ group, data = data, var.equal = TRUE)
sd(log(d_at$FirstPlace_Seconds), na.rm = TRUE)
sd(log(d_abint$FirstPlace_Seconds), na.rm = TRUE)

t.test(log(SurePlace_Seconds) ~ group, data = data, var.equal = TRUE) # *
sd(log(d_at$SurePlace_Seconds), na.rm = TRUE)
sd(log(d_abint$SurePlace_Seconds), na.rm = TRUE)
```


```{r thoughts}

leveneTest(thoughts_want ~ group, data = data)         # >
leveneTest(thoughts_not_want ~ group, data = data)     # >  
leveneTest(thoughts_amt ~ group, data = data)          # > 
leveneTest(thoughts_net ~ group, data = data)          # > 

t.test(thoughts_want ~ group,data = data, var.equal = TRUE)
sd(d_at$thoughts_want, na.rm = TRUE)
sd(d_abint$thoughts_want, na.rm = TRUE)

t.test(thoughts_not_want ~ group,data = data, var.equal = TRUE)  # **
sd(d_at$thoughts_not_want, na.rm = TRUE)
sd(d_abint$thoughts_not_want, na.rm = TRUE)

t.test(thoughts_amt ~ group,data = data, var.equal = TRUE)
sd(d_at$thoughts_amt, na.rm = TRUE)
sd(d_abint$thoughts_amt, na.rm = TRUE)

t.test(thoughts_net ~ group, data = data, var.equal = TRUE)  # ***
sd(d_at$thoughts_net, na.rm = TRUE)
sd(d_abint$thoughts_net, na.rm = TRUE)

```

```{r prep}
leveneTest(NumPrep_Total ~ group, data = data)          #   *

t.test(NumPrep_Total ~ group,data = data, var.equal = FALSE) # **
sd(d_at$NumPrep_Total, na.rm = TRUE)
sd(d_abint$NumPrep_Total, na.rm = TRUE)
```


all_des <- function(data){
  descriptives(data$Q_UPPS_NegUrgency)
  descriptives(data$Q_UPPS_PosUrgency)
  descriptives(data$Q_UPPS_Premeditation)
  descriptives(data$Q_UPPS_Perseverance)
  descriptives(data$Q_UPPS_SensationSeeking)
  
  descriptives(data$Q_BIS_1_Attention)
  descriptives(data$Q_BIS_1_Motor)
  descriptives(data$Q_BIS_1_Self_Control)
  descriptives(data$Q_BIS_1_Cognitive_Complexity)
  descriptives(data$Q_BIS_1_Preseverance)
  descriptives(data$Q_BIS_1_Cogntive_Instability)
  descriptives(data$Q_BIS_2_Attentional_Impulsiveness)
  descriptives(data$Q_BIS_2_Motor_Impulsiveness)
  descriptives(data$Q_BIS_2_Nonplanning_Impulsiveness)
  descriptives(data$Q_BIS_Total)
  
  descriptives(data$IST_FreeBlockMean_pCorrs)
  descriptives(data$IST_CostBlockMean_pCorrs)
  descriptives(data$CPTGNG_dprime_All)
  descriptives(data$CPTGNG_commission_errors)
  descriptives(data$CPTGNG_omission_errors)
  descriptives(data$MDQ_k_Final)
  descriptives(data$SSRT_sossrtInt)
  
  descriptives(data$thoughts_want)
  descriptives(data$thoughts_not_want)
  descriptives(data$thoughts_amt)
  descriptives(data$thoughts_score)
  descriptives(data$ThoughtsStart_bin)
  descriptives(data$Mull_bin)
  descriptives(data$FstMethod_bin)
  descriptives(data$FstPlace_bin)
  descriptives(data$SureMethod_bin)
  descriptives(data$SurePlace_bin)
  descriptives(data$Decision_bin)
  descriptives(data$NumPrep_Total)
  descriptives(data$X8.3_Mulled_for_this_attempt)
  descriptives(data$X1.2_Ever_made_a_plan)
  descriptives(data$X2.6_Confirm_suicide_intent)
  descriptives(data$X12.15_How_sure_want_to_die)
  descriptives(data$sis_15)
  descriptives(data$sis_7)
  descriptives(data$perceived_lethality)
  descriptives(data$X12.18_Injuries_LethalityScale)
  descriptives(data$realize_not_dead)
  
  descriptives(data$lifetimeSI_mean)
  descriptives(data$lifetimeSI_sd)
  descriptives(data$lifetimeSI_range)
  descriptives(data$lifetimeSI_onset)
  descriptives(data$lifetimeSI_duration)
  
  descriptives(data$X2.4_Aborted_Num_Times_FINAL)
  descriptives(data$aborted_onset)
  descriptives(data$aborted_duration)
  descriptives(data$aborted_freq)
  
  descriptives(data$nssi_times)
  descriptives(data$nssi_onset)
  descriptives(data$nssi_duration)
  descriptives(data$nssi_freq)
  
  descriptives(data$X2.6_Num_AT)
  descriptives(data$FirstID_to_FirstAction)
}
descriptives(d_ab$Q_BIS_1_Attention)
```
# Archived
```{r}
var_icareabout <- c("Q_UPPS_NegUrgency", "Q_UPPS_PosUrgency", "Q_UPPS_Premeditation", "Q_UPPS_Perseverance", "Q_UPPS_SensationSeeking", "Q_BIS_1_Attention", "Q_BIS_1_Motor", "Q_BIS_1_Self_Control", "Q_BIS_1_Cognitive_Complexity", "Q_BIS_1_Preseverance", "Q_BIS_1_Cogntive_Instability", "Q_BIS_2_Attentional_Impulsiveness", "Q_BIS_2_Motor_Impulsiveness", "Q_BIS_2_Nonplanning_Impulsiveness", "Q_BIS_Total", "IST_FreeBlockMean_pCorrs", "IST_CostBlockMean_pCorrs", "CPTGNG_dprime_All", "CPTGNG_commission_errors, CPTGNG_omission_errors", "MDQ_k_Final", "SSRT_sossrtInt", "thoughts_want", "thoughts_not_want", "thoughts_amt", "thoughts_score", "ThoughtsStart_bin", "Mull_bin", "FstMethod_bin", "FstPlace_bin", "SureMethod_bin", "SurePlace_bin", "Decision_bin", "NumPrep_Total", "X8.3_Mulled_for_this_attempt", "X1.2_Ever_made_a_plan", "X2.6_Confirm_suicide_intent", "X12.15_How_sure_want_to_die", "sis_15", "sis_7", "perceived_lethality", "X12.18_Injuries_LethalityScale", "realize_not_dead", "lifetimeSI_mean", "lifetimeSI_sd", "lifetimeSI_range", "lifetimeSI_onset", "lifetimeSI_duration", "X2.4_Aborted_Num_Times_FINAL", "aborted_onset", "aborted_duration", "aborted_freq", "nssi_times", "nssi_onset", "nssi_duration", "nssi_freq", "X2.6_Num_AT", "FirstID_to_FirstAction")
```
# T test
```{r}
t.test(Q_BIS_1_Attention~group, data = data)

t.test(MDQ_k_Final~group, data = data)
t.test(thoughts_not_want~group, data = data)
t.test(thoughts_score~group, data = data)
t.test(Mull_bin~group, data = data)
t.test(SurePlace_bin~group, data = data)
t.test(NumPrep_Total~group, data = data)
t.test(perceived_lethality~group, data = data)
t.test(X12.18_Injuries_LethalityScale~group, data = data)

t.test(lifetimeSI_sd~group, data = data)
t.test(lifetimeSI_range~group, data = data)
```

# ANOVA & Post hoc
```{r Compare3G}
data_4g <- rbind(d_ab, d_at, d_at_l, d_at_nl)
data_4g <- data_4g %>%
  mutate(fourGroup = ifelse(at_lethality == 1, "ab/int",
                            ifelse(at_lethality == 2.75, "at",
                                   ifelse(at_lethality == 3.625, "at_l", "at-nl"))))
data_3g_noAT <- data_4g %>%
  filter(fourGroup != "at")

summary(aov(Q_UPPS_NegUrgency~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_UPPS_NegUrgency)))                  # NO
summary(aov(Q_UPPS_PosUrgency~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_UPPS_PosUrgency)))                  # NO
summary(aov(Q_UPPS_Premeditation~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_UPPS_Premeditation)))            # NO
summary(aov(Q_UPPS_Perseverance~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_UPPS_Perseverance)))              # NO
summary(aov(Q_UPPS_SensationSeeking~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_UPPS_SensationSeeking)))      # NO

summary(aov(Q_BIS_1_Attention~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Attention)))
summary(aov(Q_BIS_1_Motor~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Motor)))
summary(aov(Q_BIS_1_Self_Control~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Self_Control)))
summary(aov(Q_BIS_1_Cognitive_Complexity~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Cognitive_Complexity)))
summary(aov(Q_BIS_1_Preseverance~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Preseverance)))
summary(aov(Q_BIS_1_Cogntive_Instability~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_1_Cogntive_Instability)))
summary(aov(Q_BIS_2_Attentional_Impulsiveness~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_2_Attentional_Impulsiveness)))
summary(aov(Q_BIS_2_Motor_Impulsiveness~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_2_Motor_Impulsiveness)))
summary(aov(Q_BIS_2_Nonplanning_Impulsiveness~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_2_Nonplanning_Impulsiveness)))
summary(aov(Q_BIS_Total~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Q_BIS_Total)))
summary(aov(IST_FreeBlockMean_pCorrs~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$IST_FreeBlockMean_pCorrs)))
summary(aov(IST_CostBlockMean_pCorrs~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$IST_CostBlockMean_pCorrs)))
summary(aov(CPTGNG_dprime_All~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$CPTGNG_dprime_All)))
summary(aov(CPTGNG_commission_errors~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$CPTGNG_commission_errors)))
summary(aov(CPTGNG_omission_errors~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$CPTGNG_omission_errors)))

summary(aov(MDQ_k_Final~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$MDQ_k_Final)))                                        # * for at-L/ab (Tukey); * for both (LSD)
PostHocTest(aov(MDQ_k_Final~fourGroup, data = data_3g_noAT), method = "lsd")
model <- aov(MDQ_k_Final~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$MDQ_k_Final))
TukeyHSD(model, ordered = TRUE)

summary(aov(SSRT_sossrtInt~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$SSRT_sossrtInt)))
summary(aov(thoughts_want~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_want)))

summary(aov(thoughts_not_want~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_not_want)))                            # * for at-L/ab (Tukey/HSD); ** for at-L/ab (LSD)
PostHocTest(aov(thoughts_not_want~fourGroup, data = data_3g_noAT), method = "lsd")
m2 <- aov(thoughts_not_want~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_not_want))
TukeyHSD(m2, ordered = TRUE)

summary(aov(thoughts_amt~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_amt)))

summary(aov(thoughts_score~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_score)))                                  # ** for at-L/ab (Tukey); ** for at-L/ab & * for at-NL/ab (LSD)
PostHocTest(aov(thoughts_score~fourGroup, data = data_3g_noAT), method = "lsd")
m3 <- aov(thoughts_score~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$thoughts_score))
TukeyHSD(m3, ordered = TRUE)

summary(aov(ThoughtsStart_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$ThoughtsStart_bin))) 
summary(aov(Mull_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Mull_bin)))                                              # ** for ab/L & ab/NL (Tukdy); *** for ab/L & ** for ab/NL (LSD)
PostHocTest(aov(Mull_bin~fourGroup, data = data_3g_noAT), method = "lsd")
m4 <- aov(Mull_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Mull_bin))
TukeyHSD(m4, ordered = TRUE)


summary(aov(FstMethod_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$FstMethod_bin)))
summary(aov(FstPlace_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$FstPlace_bin)))
summary(aov(SureMethod_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$SureMethod_bin)))
summary(aov(SurePlace_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$SurePlace_bin)))                                    # * for ab/NL (Tukey); * for ab/NL & ab/L (LSD)
PostHocTest(aov(SurePlace_bin~fourGroup, data = data_3g_noAT), method = "lsd")
m5 <- aov(SurePlace_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$SurePlace_bin))
TukeyHSD(m5, ordered = TRUE)

summary(aov(Decision_bin~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$Decision_bin)))
summary(aov(NumPrep_Total~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$NumPrep_Total)))  # * for ab/L (Tukey); ** ab/L (LSD)
PostHocTest(aov(NumPrep_Total~fourGroup, data = data_3g_noAT), method = "lsd")
m6 <- aov(NumPrep_Total~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$NumPrep_Total))
TukeyHSD(m6, ordered = TRUE)

summary(aov(X8.3_Mulled_for_this_attempt~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X8.3_Mulled_for_this_attempt)))
summary(aov(X1.2_Ever_made_a_plan~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X1.2_Ever_made_a_plan)))
summary(aov(X2.6_Confirm_suicide_intent~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X2.6_Confirm_suicide_intent)))
summary(aov(X12.15_How_sure_want_to_die~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X12.15_How_sure_want_to_die)))

summary(aov(sis_15~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$sis_15)))
summary(aov(sis_7~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$sis_7)))

summary(aov(perceived_lethality~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$perceived_lethality)))                         # * for ab/L (Tukey); ** ab/L, * for ab/NL (LSD)
PostHocTest(aov(perceived_lethality~fourGroup, data = data_3g_noAT), method = "lsd")
m7 <- aov(perceived_lethality~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$perceived_lethality))
TukeyHSD(m7, ordered = TRUE)

summary(aov(X12.18_Injuries_LethalityScale~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X12.18_Injuries_LethalityScale)))   # *** for L/NL & L/ab (Tukey & LSD)
PostHocTest(aov(X12.18_Injuries_LethalityScale~fourGroup, data = data_3g_noAT), method = "lsd")
m8 <- aov(X12.18_Injuries_LethalityScale~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X12.18_Injuries_LethalityScale))
TukeyHSD(m8, ordered = TRUE)

summary(aov(realize_not_dead~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$realize_not_dead)))

summary(aov(lifetimeSI_mean~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_mean)))

summary(aov(lifetimeSI_sd~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_sd)))                                     # ** Tukey: * ab/NL; LSD: ** ab/NL, * ab/L
PostHocTest(aov(lifetimeSI_sd~fourGroup, data = data_3g_noAT), method = "lsd")
m9 <- aov(lifetimeSI_sd~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_sd))
TukeyHSD(m9, ordered = TRUE)

summary(aov(lifetimeSI_range~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_range)))                               # ** Tukey: * for ab/L & ab/NL; LSD: ** for both
PostHocTest(aov(lifetimeSI_range~fourGroup, data = data_3g_noAT), method = "lsd")
m10 <- aov(lifetimeSI_range~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_range))
TukeyHSD(m10, ordered = TRUE)

summary(aov(lifetimeSI_onset~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_onset)))
summary(aov(lifetimeSI_duration~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$lifetimeSI_duration)))

summary(aov(X2.4_Aborted_Num_Times_FINAL~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X2.4_Aborted_Num_Times_FINAL)))
summary(aov(aborted_onset~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$aborted_onset)))
summary(aov(aborted_duration~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$aborted_duration)))
summary(aov(aborted_freq~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$aborted_freq)))

summary(aov(nssi_times~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$nssi_times)))
summary(aov(nssi_onset~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$nssi_onset)))
summary(aov(nssi_duration~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$nssi_duration)))
summary(aov(nssi_freq~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$nssi_freq)))

summary(aov(X2.6_Num_AT~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$X2.6_Num_AT)))
summary(aov(FirstID_to_FirstAction~fourGroup, data = data_3g_noAT, na.exclude(data_3g_noAT$FirstID_to_FirstAction)))
```
