---
title: "Correlation Tables for Time and Thoughts"
author: "Irene Xu"
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: true
      smooth_scroll: true
---
<br/>

**Study: Suicide Trajectory**    

The goal of this file is to create a table that summaries the correlations between time and thoughts.

<br/>
<br/>
```{r setup, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(gtsummary)
library(gt)
library(modelsummary)
library(corrplot)
source("helper_functions/apa_table_formatter.R")
source("helper_functions/effect_size_calculator.R")
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
alldata <- read_csv("../data/psai_processed_100421.csv")
```

# Select variables for the table
```{r select-var}
tt <- alldata %>%
  select(think_bin, mull_bin, dec_bin, 
         firstmethod_bin, suremethod_bin, firstplace_bin, sureplace_bin,
         thoughts_amt, thoughts_want, thoughts_not_want, thoughts_net, 
         prep_total)
```

# make 2df, all variables or concise
```{r}
tt_all <- tt %>%
  select("1. Ideation Onset" = think_bin,
         "2. Mulling Onset" = mull_bin,
         "3. Attempt Decision" = dec_bin,
         "4. Method Onset" = firstmethod_bin,
         "5. Method Decision" = suremethod_bin,
         "6. Place Onset" = firstplace_bin,
         "7. Place Decision" = sureplace_bin,
         "8. Pro-suicide Considerations" = thoughts_want,
         "9. Anti-suicide Considerations" = thoughts_not_want,
         "10. Total Considerations" = thoughts_amt,
         "11. Overall Net Considerations" = thoughts_net,
         "12. Preparatory Actions" = prep_total)

tt_concise <- tt %>%
  select("Ideation Onset" = think_bin,
         "Mulling Onset" = mull_bin,
         "Attempt Decision" = dec_bin,
         "Method Onset" = firstmethod_bin,
         "Method Decision" = suremethod_bin,
         "Place Onset" = firstplace_bin,
         "Place Decision" = sureplace_bin,
         "Pro-suicide Considerations" = thoughts_want,
         "Anti-suicide Considerations" = thoughts_not_want,
         "Total Considerations" = thoughts_amt,
         "Overall Net Considerations" = thoughts_net,
         "Preparatory Actions" = prep_total)
```

# make table for all var cor (original version, no **)
```{r}
cor <- datasummary_correlation(tt_all, output = "gt", align = "lllllllllllll") 
cor <- cor %>% 
  cols_width(everything() ~ px(60)) %>%
  tab_options(table.font.size = 14) %>%
  cols_width("1. SI Onset" ~ px(50),
         "2. Start to Mull" ~ px(50),
         "3. Decide to Attempt" ~ px(50),
         "4. Start to Consider Method" ~ px(50),
         "5. Decide on Method" ~ px(50),
         "6. Start to Consider Place" ~ px(50),
         "7. Decide on Place" ~ px(50),
         "8. Pro-suicide Considerations" ~ px(50),
         "9. Anti-suicide Considerations" ~ px(50),
         "10. Total Considerations" ~ px(50),
         "11. Overall Net Considerations" ~ px(50),
         "12. Preparatory Actions" ~ px(50),
         everything() ~ px(190)) %>%
  cols_label("1. SI Onset" = "1",
         "2. Start to Mull" = "2",
         "3. Decide to Attempt" = "3",
         "4. Start to Consider Method" = "4",
         "5. Decide on Method" = "5",
         "6. Start to Consider Place" = "6",
         "7. Decide on Place" = "7",
         "8. Pro-suicide Considerations" = "8",
         "9. Anti-suicide Considerations" = "9",
         "10. Total Considerations" = "10",
         "11. Overall Net Considerations" = "11",
         "12. Preparatory Actions" = "12") %>%
  apa_cor_formatter("", 85)
gtsave(cor, "cor_matrix_all.png", "../tables/")
```

# make table for all (with **)
```{r}
big_matrix <- correlation_matrix(tt_all, use = "lower", replace_diagonal =TRUE, replacement = "-")
big_matrix <- as.data.frame(big_matrix)
for (i in 1:12) {
  names(big_matrix)[i] <- i
}
big_matrix$` ` <- rownames(big_matrix)

all_cor <- big_matrix[, c(13,1,2,3,4,5,6,7,8,9,10,11)]
all_cor_table <- all_cor %>%
  gt() %>%     
  apa_cor_formatter("", 100)
gtsave(all_cor_table, "cor_matrix_all.png", "../tables/")
```

# Correlation Matrix for all variables with corrplot
```{r fig.width=3,fig.height=3}
tt.cor = cor.mtest(tt)
corrplot(cor(tt, use = "complete.obs"), method = "number", type = "upper", order = "hclust",
         tl.col = "black", tl.srt = 50)
```

# Concise table for correlations between time and considerations
```{r}
matrix <- correlation_matrix(tt_concise, use = "lower", replace_diagonal =TRUE, replacement = "-")
concise_matrix <- as.data.frame(matrix[8:12, 1:7])
concise_matrix$` ` <- rownames(concise_matrix)

concise_cor <- concise_matrix[, c(8,1,2,3,4,5,6,7)]
concise_cor_table <- concise_cor %>%
  gt() %>%     
  apa_cor_formatter("", 100)
gtsave(concise_cor_table, "cor_matrix_concise.png", "../tables/")
```

