---
title: "Demographics"
author: "Irene Xu"
date: "Last updated: `r Sys.Date()`"
output:
  html_document:
    theme: yeti
    code_folding: hide
    toc: true
    toc_depth: 5
    toc_float:
      collapsed: true
      smooth_scroll: true
---
<br/>

**Study: Suicide Trajectory**    

The goal of this file is to create tables that show the demographic breakdown of the sample.

<br/>
<br/>
```{r setup, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(hrbrthemes)
library(gtsummary)
library(gt)
source("helper_functions/effect_size_calculator.R")
source("helper_functions/apa_table_formatter.R")
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
alldata <- read_csv("../data/psai_processed_100421.csv")
```

# Select variables for the table
```{r}
demographics <- alldata %>%
  select(group, age, sex, race, education, student)
```

# Create and save the table
```{r}
reset_gtsummary_theme()
theme_gtsummary_compact()

demographics$education <- factor(demographics$education, levels = c("Less than high school", "High school graduate", "1-3 years of college", "College graduate", "Professional degree"))
demographics$student <- factor(demographics$student, levels = c("Student", "Not a student"))

t1 <- demographics %>% 
  tbl_summary(
    by = group,    
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_continuous() ~ 2,
    label = list(
      age ~ "Age",
      sex ~ "Sex",
      race ~ "Race",
      education ~ "Educational Attainment",
      student ~ "Whether a student"),
    missing_text = "(Missing)") %>%
  modify_header(
    list(
      label ~ "",
      stat_1 ~ '**Aborted/Interrupted**, N = {n}',
      stat_2 ~ '**Actual**, N = {n}'
      )) %>%
  modify_spanning_header(all_stat_cols() ~ "**Type of the Most Recent Attempt**") %>%
  bold_labels() %>%
  add_p() %>%
  as_gt() %>%
  gt::opt_align_table_header(align = "left") %>%
  apa_table_formatter("Demographic Information", 50)

gt::gtsave(t1, "table1_demographics.png", "../tables/")
```

# Other things to consider
1. add a distribution of age  
* For age, the ab/int group are more skewed to the younger side
* The majority of the sample falls between 18-25
```{r}
ggplot(demographics, aes(x = age, color = group, fill = group)) + 
  geom_density(alpha = 0.5)
```

```{r}
demographics <- demographics %>%
  mutate(
    age_group = 
      ifelse(age <= 25, "18-25",
      ifelse(age > 35, "> 35", "26-35")))

demographics$age_group <- factor(demographics$age_group, levels = c("18-25", "26-35", "> 35"))
demographics %>% 
  tbl_summary(
    by = group,    
    statistic = all_continuous() ~ "{mean} ({sd})",
    digits = all_continuous() ~ 2,
    label = list(
      age ~ "Age",
      sex ~ "Sex",
      race ~ "Race",
      education ~ "Educational Attainment",
      student ~ "Whether a student"),
    missing_text = "(Missing)") %>%
  modify_header(
    list(
      label ~ "",
      stat_1 ~ '**Aborted/Interrupted**, N = {n}',
      stat_2 ~ '**Actual**, N = {n}'
      )) %>%
  modify_spanning_header(all_stat_cols() ~ "**Types of Attempts Made**") %>%
  bold_labels() %>%
  add_p() %>%
  as_gt() %>%
  gt::opt_align_table_header(align = "left") %>%
  tab_header(title = "Table 1. Demographic Information")
```

2. add percentage made an aborted, ever nssi
